### 2012-07-17 paper/chemokine.tex
Getting ready for distribution to outside readers

\begin{table}
\begin{tabular}{ | c | c | c | }
  \hline                        
  Paramter & Value & Source \\
  \hline
  Viral Diffusion & .0318 & \cite{Beauchemin2006} \\
  Viral Decay &  $1/day$ & Soumya \\
  Chemokine Diffusion & $.318 \mu m^2/s$ & \cite{Beauchemin2006} \\
  Chemokine Decay &  $3.8508e-4/s$ & 30m half-life \\
  Infection Sensitivity &  $2 h/virion$ & [1*] \\
  Incubation Time &  $10 h$ & \cite{Mitchell2011} \\
  Expression Time &  $16.7 h$ & \cite{Mitchell2011} \\
  Apoptosis Time & $1 h$ & Fred \\
  T-Cell Production Rate & $777/h$ & Soumya, Miao fits \\ 
  Circulation Time & $6 m$ & Fred, mouse model \\
  Search Time & $10 m$ & Fred, mouse model \\
  T-Cell Speed (Search) & $30 \mu m/s$ & Fred ? \\
  T-Cell Speed (Activated) & $3 \mu m/s$ & Fred ?\\
  T-Cell Sensitivity & $1 ng/mL$ & \cite{Gao2003} \\
  T-Cell Expected Kill Rate & $10 m$ & Fred/Drew \\
  Cell Radius & $25 \mu m$ & Drew? \\
  T-Cell Age (Active) & $2 h$ & Fred \\
  T-Cell Age (Other) & $3 d$ & Fred \\
  T-Cell Ramp Up Time & $5 d$ & \cite{Banerjee2011} \\
  IgM Strength & Viral decay of $3/day$ after day 3 & Soumya [3*] \\
  \hline  
\end{tabular}
\caption{Generic model parameters}
\label{table:parameters}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ | r | c | c | }
  \hline                        
  Paramter & Value & Source \\
  \hline
  IP-10 Production Rate &  & [2*]\\
  Avian H5N1 & 2.0e-4 pg/s$\cdot$cell & \\
  Seasonal H1N1 & 1.8e-4 pg/s$\cdot$cell& \\
  Pandemic H1N1 & 8.7e-5 pg/s$\cdot$cell& \\
  \hline
  RANTES Production Rate & & [2*] \\
  Avian H5N1 & 1.3e-5 pg/s$\cdot$cell& \\
  Seasonal H1N1 & 8.9e-7pg/s$\cdot$cell& \\
  Pandemic H1N1 & 4.4e-6 pg/s$\cdot$cell& \\
  \hline
  Virus Production Rate &  & \cite{Mitchell2011} \\
  Avian H5N1 & 5.4e-5 PFU/s$\cdot$cell& \\
  Seasonal H1N1 & 3.8e-4 PFU/s$\cdot$cell& \\
  Pandemic H1N1 & 5.1e-3 PFU/s$\cdot$cell& \\  
  \hline  
\end{tabular}
\caption{Strain specific model parameters}
\label{table:strains}
\end{center}
\end{table}

\begin{itemize}
\item[1] The molecular concentration where there is one molecule per eptithelial cell volume is 1.53e-17 mol/mL.  Thus, if you multiply the local viral concentration by 9.05e12 you get an infection event after two hours given that concentration.  This probability scales linearly with the viral concentration.
\item[2] These are calculated off of Fred's new data sets using the Mitchell ODE model and parameters as a basis.
\item[3] IgM is represented by increasing the viral decay rate to 3/day after the third day of the simulation.
\end{itemize}

@@

\begin{figure}[ht!]
\begin{center}
 \includegraphics[width=\textwidth]{variance}
 \end{center}
\caption{Model results: Time series plots of ten runs of aH5N1 (A), sH1N1 (B), and pH1N1 (C) infections. IP-10 and RANTES were simulated in each run, except for aH5N1, which  produced only RANTES.  The ten runs were initialized identically for each strain.  Each simulation was run with identical T-cell sensitivity to chemokine (100 ng/mL).} 
 \label{fig:variance}
\end{figure}

@@

>>>>

\begin{table}
\begin{tabular}{ | c | c | c | }
  \hline                        
  Paramter & Value & Source \\
  \hline
  Viral Diffusion & .0318 & \cite{Beauchemin2006} \\
  Viral Decay &  $1/day$ & Phenomenological \\
  Chemokine Diffusion & $.318 \mu m^2/s$ & \cite{Beauchemin2006} \\
  Chemokine Decay &  $3.8508e-4/s$ & 30m half-life \\
  Infection Sensitivity &  $2 h/virion$ & Phenomenological \\
  Incubation Time &  $10 h$ & \cite{Mitchell2011} \\
  Expression Time &  $16.7 h$ & \cite{Mitchell2011} \\
  Apoptosis Time & $1 h$ & Phenomenological \\
  T-Cell Production Rate & $777/h$ & \cite{Miao2010} \\ 
  Circulation Time & $6 m$ & \cite{Banerjee2010b} \\
  Search Time & $10 m$ & \cite{Banerjee2010b} \\
  T-Cell Speed (Search) & $30 \mu m/s$ & \cite{Miller2003} \\
  T-Cell Speed (Activated) & $3 \mu m/s$ & \cite{Miller2003} \\
  T-Cell Sensitivity & $1 ng/mL$ & \cite{Gao2003} \\
  T-Cell Expected Kill Rate & $10 m$ & Fred/Drew \\
  Cell Radius & $25 \mu m$ & Phenomenological \\
  T-Cell Age (at FOI) & $2 h$ & [REF] \\
  T-Cell Age (Other) & $3 d$ & [REF] \\
  T-Cell Ramp Up Time & $5 d$ & \cite{Banerjee2011} \\
  IgM Strength & Viral decay of $3/day$ & Phenomenological \\
  \hline  
\end{tabular}
\caption{Generic model parameters}
\label{table:parameters}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ | r | c | c | }
  \hline                        
  Paramter & Value & Source \\
  \hline
  IP-10 Production Rate &  & ODE Fits \\
  Avian H5N1 & 2.0e-4 pg/s$\cdot$cell & \\
  Seasonal H1N1 & 1.8e-4 pg/s$\cdot$cell& \\
  Pandemic H1N1 & 8.7e-5 pg/s$\cdot$cell& \\
  \hline
  RANTES Production Rate & & ODE Fits \\
  Avian H5N1 & 1.3e-5 pg/s$\cdot$cell& \\
  Seasonal H1N1 & 8.9e-7pg/s$\cdot$cell& \\
  Pandemic H1N1 & 4.4e-6 pg/s$\cdot$cell& \\
  \hline
  Virus Production Rate &  & \cite{Mitchell2011} \\
  Avian H5N1 & 5.4e-5 PFU/s$\cdot$cell& \\
  Seasonal H1N1 & 3.8e-4 PFU/s$\cdot$cell& \\
  Pandemic H1N1 & 5.1e-3 PFU/s$\cdot$cell& \\  
  \hline  
\end{tabular}
\caption{Strain specific model parameters}
\label{table:strains}
\end{center}
\end{table}

@@

\begin{figure}[ht!]
\begin{center}
 \includegraphics[width=\textwidth]{variance}
 \end{center}
\caption{Model results: Time series plots of fifty runs of aH5N1 (A), sH1N1 (B), and pH1N1 (C) infections (gray). IP-10 and RANTES were simulated in each run, except for aH5N1, which  produced only RANTES.  Each run was initialized identically for each strain.  The middle line shows the average while the outer lines show the 95\% confidence interval.} 
 \label{fig:variance}
\end{figure}

@@

Our model combines the dynamics of human epithelial tissue with the scaling of a mouse's immune system.  We choose to use mouse scale models because of the computational limitations of our ABM.  By limiting our model to mice, we are able to keep the active agent population below 100,000, which allows a single model to be run in less than a day.  A human-sized model would be computationally intractable.  We find this practice acceptable for two reasons.  First, the size differences and scaling principles between mice and human has been well documented [REF?] and can be accounted for.  Second, this paper focuses on relative differences between strains so an exact recreation of the immune response is not necessary.

In our model, the ability of T-cells to detect a chemokine signal and their subsequent motility upon doing so rests entirely on the T-cell's sensitivity to chemokine parameter.  Once a T-cell encounters a concentration of chemokine above the sensitivity threshold it will immediately climb the chemotactic gradient to the local maxima.  Studies of T-cell chemotaxis show that T-cell movement depends more on the magnitude of the chemokine gradient rather than the concentration \cite{Gao2003}.  Furthermore, T-cells will perform a biased random walk rather than moving in a straight line directly up the concentration gradient [REF?].  We experimented with biased random walks in our model and noticed no change in any results.  Thus, we chose to keep the model simple and limited T-cell movement to directly climbing the chemokine gradient.
